Xor-Some Preregistered Study: Analyses

### 2021-11-14 analysis/main/01_xor-some_prereg_preprocessing_final.Rmd
add N206, correlations, fix priors exploration, set up writing

# get participants failing comprehension questions
d_test <- d_test %>%
  group_by(submission_id) %>%
  mutate(passed_filler_trial = case_when(test_condition == "true" ~ response >= 60,
                                   test_condition == "false" ~ response <= 40,
                                   test_condition == "uncertain" ~ response %in% (10:90)),
         mean_comprehension = mean(passed_filler_trial),
         passed_filler = mean_comprehension >= 0.8
         )

@@

cat(" Nr. of participants left after cleaning: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())
```
Exclude the 201st participant for target N=200:
```{r, results='hide'}
d_full_clean %>% arrange(., desc(submission_id)) %>% distinct() %>% pull(submission_id)

# exclude participant with last submission_id
d_full_clean <- d_full_clean %>% filter(submission_id != 2620)

cat(" Nr. of participants left after cleaning and N=200 extraction: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())

@@

d_critical_zScored_wide <- d_critical_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered) %>% 
  unique() %>% 
  pivot_wider(
    names_from = block_extended, 
    values_from = response_centered, 
    values_fn = mean # getting means for double prior measurement in "xor"
  ) 
```

Write out z-scored data
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
```

>>>>

# get participants failing comprehension questions
# Perform exclusions based on comprehension question EXCLUDING the test_false1 question from the vignette
# with the ID=64 which had an incorrect prior classification.
d_test <- d_test %>%
  group_by(submission_id) %>%
  filter(ID != 64 && test_question != "test_false1") %>%
  mutate(passed_filler_trial = case_when(test_condition == "true" ~ response >= 60,
                                   test_condition == "false" ~ response <= 40,
                                   test_condition == "uncertain" ~ response %in% (10:90)),
         mean_comprehension = mean(passed_filler_trial),
         passed_filler = mean_comprehension >= 0.8
         )

@@

cat(" Nr. of participants left after cleaning: ", d_full_clean %>% distinct(submission_id) %>% pull() %>% length())
```
[-Exclude the 201st participant for target N=200-]
The exclusion of the last participant isn't necessary anymore, since we only have 200 subjects left upon exclusions due to the initially incorrect native language check.

@@

d_critical_zScored_wide <- d_critical_zScored %>% 
  select(submission_id, title, main_type, block_extended, response_centered) %>% 
  unique() %>% 
  pivot_wider(
    names_from = block_extended, 
    values_from = response_centered, 
    values_fn = mean # getting means for double prior measurement in "xor"
  )

```{r}
# create labels for first vs second prior question, order-based 
d_critical_zScored %>% 
  filter(block != "xor" & block != "some") %>%
  filter(block == class_condition) %>%
  filter(block == "prior", main_type == "xor") %>%
  ungroup() %>%
  mutate(priorQ_nr = rep(c(1,2), times=nrow(.)/2),
         priorQ_factor = paste("prior", priorQ_nr, sep = "_"),
         unique_ID = paste(submission_id, ID, sep="_")) -> d_xor_priors

# create labels for the two questions
d_xor_priors %>% group_by(ID, prompt) %>%
  select(ID, prompt) %>% distinct() %>%
  ungroup() %>%
  mutate(
    priorQ_label = rep(c("priorQ_1", "priorQ_2"), 32)
  ) -> d_xor_priors_labels

d_xor_priors_labels_full <- left_join(d_xor_priors, d_xor_priors_labels, by = c("prompt", "ID")) %>% 
  select("prompt", "ID", "block_extended", "class_condition", "submission_id", "priorQ_factor", "priorQ_label")

# create a df with both prior ratings for exploratory analysis
d_critical_zScored_xor <- d_critical_zScored %>%
  ungroup() %>%
  filter(main_type == "xor") %>%
  select(submission_id, title, main_type, block_extended, response_centered, prompt, ID, class_condition) %>% 
  unique() %>% 
  left_join(., d_xor_priors_labels_full, 
            by = c("prompt", "ID", "block_extended", "class_condition", "submission_id")
            ) %>%
  filter(block_extended == class_condition | block_extended == "target") %>%
  mutate(
    block_xor_order = ifelse("prior" == block_extended, priorQ_factor, block_extended),
    block_xor_type = ifelse("prior" == block_extended, priorQ_label, block_extended),
  ) %>% select(-priorQ_factor, -priorQ_label)

# create wide version for the order based question distinction
d_critical_zScored_wide_xor_prior_order <- d_critical_zScored_xor %>% 
  select(-block_extended, -block_xor_type, -class_condition, -prompt) %>%
  unique() %>%
  pivot_wider(
    names_from = block_xor_order, 
    values_from = response_centered
  )

# create wide version for the type based question distinction
d_critical_zScored_wide_xor_prior_type <- d_critical_zScored_xor %>% 
  select(-block_extended, -block_xor_order, -class_condition, -prompt) %>%
  unique() %>%
  pivot_wider(
    names_from = block_xor_type, 
    values_from = response_centered
  ) 
```

Write out z-scored data:
```{r}
d_critical_zScored %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_critical_zScored_wide %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")

# write out dataframes wth xor priors
d_critical_zScored_wide_xor_prior_order %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-order.csv")

d_critical_zScored_wide_xor_prior_type %>% write_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-type.csv")

### 2021-11-14 analysis/main/02_xor-some_prereg_plots_final.Rmd
add N206, correlations, fix priors exploration, set up writing

Read data created in preprocessing script:
```{r, warning=FALSE, message=FALSE, results='hide'}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_test <- read_csv("./../../data/main/results_prereg_raw_final_test.csv")
```

@@

>>>>

Read data created in preprocessing script:
```{r, warning=FALSE, message=FALSE, results='hide'}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
d_test <- read_csv("./../../data/main/results_prereg_raw_final_test.csv")
d_critical_zScored_wide_xor_priors_order <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-order.csv")
d_critical_zScored_wide_xor_priors_type <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-type.csv")
```

@@

Plot the pairwise correlations of the predictors and the inference rating for "some": 
```{r, message=FALSE, warning=FALSE}
GGally::ggpairs(
  filter(d_critical_zScored_wide, main_type == "some") %>% ungroup() %>%  
    select(prior, competence, relevance, target)
)
```

Plot the pairwise correlations of the predictors and the inference rating for "or", by order of presentation of the two prior questions:
```{r, message=FALSE, warning=FALSE}
# correlation plot for "or"
GGally::ggpairs(
  filter(d_critical_zScored_wide_xor_priors_order, main_type == "xor") %>%  ungroup() %>%
    select(prior_1, prior_2, competence, relevance, target)
  )
```

Plot the pairwise correlations of the predictors and the inference rating for "or", by type of prior questions:
```{r, message=FALSE, warning=FALSE}
# correlation plot for "or"
GGally::ggpairs(
  filter(d_critical_zScored_wide_xor_priors_type, main_type == "xor") %>%  ungroup() %>%
    select(priorQ_1, priorQ_2, competence, relevance, target)
  )
```

### 2021-11-14 analysis/main/03_xor-some_prereg_analysis_final.Rmd
add N206, correlations, fix priors exploration, set up writing

Read data created in preprocessing script:
```{r, message=FALSE, warning=FALSE, results='hide'}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")
```

@@

>>>>

Read data created in preprocessing script:
```{r, message=FALSE, warning=FALSE, results='hide'}
d_critical_zScored_wide <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide.csv")
d_critical_zScored <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_long.csv")

d_critical_zScored_wide_xor_prior_order <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-order.csv")

d_critical_zScored_wide_xor_prior_type <- read_csv("./../../data/main/results_prereg_tidy_final_zScored_wide_xor_priors-type.csv")
```

@@

A non-preregistered, but nevertheless possibly interesting exploratory analysis including the two individual prior ratings of the conditionals in the xor condition as predictors (as opposed to the mean of the two used in the preceding models):
Analysis based on the order of appearance of the questions:
```{r, results='hide', message=FALSE, warning=FALSE}

model_xor_priors_order <- brm(target ~ prior_1*prior_2*competence*relevance +
                   (1 + prior_1 + prior_2 + competence + relevance || submission_id) +
                   (1 | title),
                 data = d_critical_zScored_wide_xor_prior_order,
                 prior = priors,
                 sample_prior = T,
                 control = list(adapt_delta = 0.95),
                 cores = 4,
                 iter = 3000)
```

```{r}
summary(model_xor_priors_order)
```

Check the intervals of intervals, computing them separately using only one prior estimate, to see if we get different results:
```{r}
model_xor_priors_order %>% spread_draws(b_Intercept, b_prior_1, b_prior_2, b_competence, b_relevance) %>% 
  mutate(
    prior1_xor = b_prior_1,
    prior2_xor = b_prior_2,
    competence_xor = b_competence,
    relevance_xor =  b_relevance
  ) -> model_xor_priors_posteriors

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_xor_priors_order <- model_xor_priors_posteriors %>% 
  select(prior1_xor, prior2_xor, 
         competence_xor, relevance_xor) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_xor_priors_order
```

Prior question type based analysis:
```{r, results='hide', message=FALSE, warning=FALSE}

model_xor_priors_type <- brm(target ~ priorQ_1*priorQ_2*competence*relevance +
                   (1 + priorQ_1 + priorQ_2 + competence + relevance || submission_id) +
                   (1 | title),
                 data = d_critical_zScored_wide_xor_prior_type,
                 prior = priors,
                 sample_prior = T,
                 control = list(adapt_delta = 0.95),
                 cores = 4,
                 iter = 3000)
```

```{r}
summary(model_xor_priors_type)
```

Check the intervals of intervals, computing them separately using only one prior estimate, to see if we get different results:
```{r}
model_xor_priors_type %>% spread_draws(b_Intercept, b_priorQ_1, b_priorQ_2, b_competence, b_relevance) %>% 
  mutate(
    priorQ1_xor = b_priorQ_1,
    priorQ2_xor = b_priorQ_2,
    competence_xor = b_competence,
    relevance_xor =  b_relevance
  ) -> model_xor_priors_posteriors

# check P that the effects are positive / negative / no effect present
posterior_hypotheses_xor_priors_type <- model_xor_priors_posteriors %>% 
  select(priorQ1_xor, priorQ2_xor, 
         competence_xor, relevance_xor) %>%
  gather(key, val) %>%
  group_by(key) %>% mutate(positive = mean(val > 0.05),
                           negative = mean(val < -0.05),
                           no = mean(val %>% between(-0.05, 0.05))) %>%
  summarise(positive_eff = mean(positive),
            negative_eff = mean(negative),
            no_eff = mean(no))
posterior_hypotheses_xor_priors_type
```
